### 2020-02-27 paper/4_simulation.tex
Deprecated: Diagonalization of DS as LP

However, it turns out direct implementation of Algorithm 8 exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
Fortunately, they have briefly pointed out, complex DS can be recast as an second-order cone program (SOCP), and SOCP is one of the several standard convex programming problems for which there are already numerous efficient algorithms.

Before describing the recast, for ease of treatment we would like to represent complex vector and matrices by real, extended vectors and matrices.
\Result
{Definition}
{
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injectivity is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
\Result
{Definition}
{
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}
}

@@

\startsection [title={Second Order Cone Programming}]

We shall see furthermore that the program can be cast into an SOCP.
To make the point clearer, we rewrite the program just above into an extended block matrix form, by defining auxiliary variables as follows,
%
\DispNum {t:::01:Nh} {
\NC \V {t}
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {1} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
%
\NC \V {x}'
= \NC \startTheMatrix
\NC \T {\V {g}}' \NR
\NC \V {m} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
}
%
with
%
\DispNum {A:i:Ui:h1} {
\NC \M {A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
%
\NC \V {b}_i
= \NC \V {0}
\in \MB {R} ^{2 N_H^2} \NR
%
\NC \V {c}_i
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
%
\NC d_i
= \NC 0 \NR
%
\NC i 
= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
}

And
%
\DispNum {A:i:Ui:h1} {
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
\in \MB {R} ^{2 N_H^2} \NR
%
\NC \V {c}_i
= \NC \V {0}
\in \MB {R} ^{3 N_H^2} \NR
%
\NC d_i
= \NC \g_{\Rm {DS}} \NR
%
\NC i 
= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
}
%
\Result
{Algorithm}
{
\startitemize[n]
%
\item Input \m {\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
%
\item Calculate
%
\DispNum {x:::mi:h1} {
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}' \in \MB {C} ^{N_H^2}}
\MC \IP {\V {t}, \V {x}'} \NR
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
\NC \MC i 
=0, 1, 2, \ldots, 2 N_H^2 -1 \NR
\stopcases \NR
}
%
\item Extract
%
\DispNum {g:::x0:h1} {
\NC \Hat {\T {\V {g}}}
\LA \NC \Hat {\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
}
%
\item Convert 
%
\DispNum {g:::R1:1g} {
\NC \Hat {\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat {\T {\V {g}}}} \NR
}
%
\item Find \m {\Hat {G}} by
%
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
%
\item Find \m {\Hat {\M {H}}} by
%
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
%
\item Output \m {\Hat {\M {H}}}.
%
\stopitemize
}

@@

\startsubsection [title={Transformation by Diagonalization}]

By Real Spectral Theorem, \m {\M {P} ^\Tr \M {P}} can be diagonized.
Let
\Disp {
\NC \M {P} ^\Tr \M {P}
= \NC \M {Q} \M {D} \M {Q} ^\Tr \NR
}
where
\Disp {
\NC \M {Q} ^\Tr \M {D} \M {Q}
= \NC I \NR
}
It can be seen that only \m {2N_Y^2} of \m {2N_H^2} singular values are nonzero.
Without loss of generality, suppose
\Disp {
\NC \MB {R} ^{2 N_H^2}
= \NC \MS {U} \oplus \MS {V} \NR
}
with
\Disp {
\NC \Rm {dim} \; \MS {U}
= \NC 2 N_Y^2 \NR
\NC \Rm {dim} \; \MS {V}
= \NC 2 N_H^2 -2 N_Y^2 \NR
}
such that
\Disp {
\NC \M {D}
= \NC \startTheMatrix
\NC \DU, \NC \M {0} \NR
\NC \M {0}, \NC \M {0} \NR
\stopTheMatrix \NR
}

Suppose
\Disp {
\NC \V {g}
= \NC \gp - \gm \NR
}
with
\Disp {
\NC -\gp
\preceq \NC 0 \NR
\NC -\gm
\preceq \NC 0 \NR
}
Introduce
\Disp {
\NC \fp
= \NC \M {Q} ^\Tr \gp \NR
\NC \fm
= \NC \M {Q} ^\Tr \gm \NR
}
If we define
\Disp {
\NC \fp
= \NC \fpU + \fpV \NR
\NC \fm
= \NC \fmU + \fmV \NR
}
That is, taking components of \m {\fp, \fm} respectively in \m {\MS {U}, \MS {V}}.
Then we see that
\Disp {
\NC \fpU
= \NC \QU ^\Tr \gp \NR
\NC \fmU
= \NC \QU ^\Tr \gm \NR
\NC \fpV
= \NC \QV ^\Tr \gp \NR
\NC \fmV
= \NC \QV ^\Tr \gm \NR
}
Here \m {\QU ^\Tr} is the abbreviation of \m {\RB {\QU} ^\Tr}.

Notice that the constraint
\Disp {
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}}
\preceq \NC \g \V {1} \NR
}
can be written as
\Disp {
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} + \sp
= \NC \V {0} \NR
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} - \sm
= \NC \V {0} \NR
}
with
\Disp {
\NC -\sp
\preceq \NC 0 \NR
\NC -\sm
\preceq \NC 0 \NR
}

Now, define
\Disp {
\NC \kpU
= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
\NC \kmU
= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
\NC \kpV
= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
\NC \kmV
= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
}

@@

>>>>

However, it turns out direct implementation of Algorithm 8 exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
Fortunately, they have briefly pointed out, complex DS can be recast as an linear program (LP),
one of the basic convex programming problems for which there are already numerous efficient algorithms.
Moreover, we show that this LP can be recast to another form with the total dimension of variables reduced.

Before that, we again introduce some notation.
We want to represent complex vector and matrices by real vectors and matrices, as follows.
\Result
{Definition}
{
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injectivity is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
\Result
{Definition}
{
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}
}

@@

\startsubsection [title={Transformation into Linear Program}]

Next, we define some auxiliary variables, and prepare to rewrite Program ().
The first idea is that \m {\V {g}} can be split into positive and negative parts, making the \m {\ell}-1 norm target function into a inner product, and this already makes Algorithm () a LP, just as noted by Tao [].
The second idea is that, by Real Spectral Theorem, \m {\M {P} ^\Tr \M {P}} can be diagonized, and with suitable choice of variables, we may greatly reduce the overhead due to Newton step.
This has not been remarked on the literature as far as we know.

As pointed out above, let
\Disp {
\NC \M {P} ^\Tr \M {P}
= \NC \M {Q} \M {D} \M {Q} ^\Tr \NR
}
where
\Disp {
\NC \M {Q} ^\Tr \M {Q}
= \NC I \NR
}
It can be seen that only \m {2N_Y^2} of \m {2N_H^2} singular values are nonzero.
Without loss of generality, suppose
\Disp {
\NC \MB {R} ^{2 N_H^2}
= \NC \MS {U} \oplus \MS {V} \NR
}
with
\Disp {
\NC \Rm {dim} \; \MS {U}
= \NC 2 N_Y^2 \NR
\NC \Rm {dim} \; \MS {V}
= \NC 2 N_H^2 -2 N_Y^2 \NR
}
such that
\Disp {
\NC \M {D}
= \NC \startTheMatrix
\NC \DU, \NC \M {0} \NR
\NC \M {0}, \NC \M {0} \NR
\stopTheMatrix \NR
}

Suppose
\Disp {
\NC \V {g}
= \NC \gp - \gm \NR
}
with
\Disp {
\NC -\gp
\preceq \NC 0 \NR
\NC -\gm
\preceq \NC 0 \NR
}
Introduce
\Disp {
\NC \fp
= \NC \M {Q} ^\Tr \gp \NR
\NC \fm
= \NC \M {Q} ^\Tr \gm \NR
}
If we define
\Disp {
\NC \fp
= \NC \fpU + \fpV \NR
\NC \fm
= \NC \fmU + \fmV \NR
}
That is, taking components of \m {\fp, \fm} respectively in \m {\MS {U}, \MS {V}}.
Note that
\Disp {
\NC \fpU
= \NC \QU ^\Tr \gp \NR
\NC \fmU
= \NC \QU ^\Tr \gm \NR
\NC \fpV
= \NC \QV ^\Tr \gp \NR
\NC \fmV
= \NC \QV ^\Tr \gm \NR
}
Here \m {\QU ^\Tr} is the abbreviation of \m {\RB {\QU} ^\Tr}.

Notice that the constraint
\Disp {
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}}
\preceq \NC \g \V {1} \NR
}
can be written as
\Disp {
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} + \tp
= \NC \V {0} \NR
\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} + \g \V {1} - \tm
= \NC \V {0} \NR
}
for some \m {\tp, \tm} with
\Disp {
\NC -\tp
\preceq \NC 0 \NR
\NC -\tm
\preceq \NC 0 \NR
}

Now, define
\Disp {
\NC \kp
= \NC \M {Q} ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
\NC \km
= \NC \M {Q} ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
}
and that, similarly,
\Disp {
\NC \kp
=\NC \kpU + \kpV \NR
\NC \km
=\NC \kmU + \kmV \NR
}
Again, allow us write it out for clarity that
\Disp {
\NC \kpU
= \NC \QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
%
\NC \kmU
= \NC \QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
%
\NC \kpV
= \NC \QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
%
\NC \kmV
= \NC \QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
}
And () becomes
\Disp {
\NC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tp - \kpU
=\NC 0 \NR
%
\NC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tm - \kmU
=\NC 0 \NR
%
\NC \QV ^\Tr \tp - \kpV
=\NC 0 \NR
%
\NC \QV ^\Tr \tm - \kmV
=\NC 0 \NR
}

Our target function, in terms of new variables, reads
\Disp {
\NC \VNm {\V {g}} _1
=\NC \IP {\V {1}, \gp} - \IP {\V {1}, \gm} \NR
%
\NC =\NC \IP {\M {Q} ^\Tr \V {1}, \fp} - \IP {\M {Q} ^\Tr \V {1}, \fm} \NR
%
\NC =\NC \IP {\M {Q} ^\Tr \V {1}, \fpU} - \IP {\M {Q} ^\Tr \V {1}, \fmU}
+ \IP {\M {Q} ^\Tr \V {1}, \fpV} - \IP {\M {Q} ^\Tr \V {1}, \fmV} \NR
}

This way, the matrix whose Hessian is required by Newton step would be much more sparse (Boyd p.565)

\Result
{Algorithm}
{
\startitemize[n]
%
\item Input \m {\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
%
\item Solve the convex program
%
\DispNum {x:::mi:h1} {
\NC \startcases
\NC \MC \fpU, \fpV, \fmU, \fmV, \sp, \sm: \NR
%
\NC \min
\MC \IP {\M {Q} ^\Tr \V {1}, \fpU}
- \IP {\M {Q} ^\Tr \V {1}, \fmU}
+ \IP {\M {Q} ^\Tr \V {1}, \fpV}
- \IP {\M {Q} ^\Tr \V {1}, \fmV} \NR
%
\NC \Rm {subject} \; \Rm {to} \Q
\MC -\QU \fpU -\QV \fpV \preceq 0 \NR
%
\NC \MC -\QU \fmU -\QV \fmV \preceq 0 \NR

\NC \MC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tp - \kpU = 0 \NR
%
\NC \MC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tm - \kmU = 0 \NR
%
\NC \MC \QV ^\Tr \tp - \kpV = 0 \NR
%
\NC \MC \QV ^\Tr \tm - \kmV = 0 \NR
%
\NC \MC -\tp \preceq 0 \NR
%
\NC \MC -\tm \preceq 0 \NR
\stopcases \NR
}
%
\item Extract
%
\DispNum {g:::x0:h1} {
\NC \Hat {\T {\V {g}}}
\LA \NC \Hat {\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
}
%
\item Convert \m {\Hat {\V {g}}} by
%
\DispNum {g:::R1:1g} {
\NC \Hat {\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat {\T {\V {g}}}} \NR
}
%
\item Find \m {\Hat {G}} by
%
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
%
\item Find \m {\Hat {\M {H}}} by
%
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
%
\item Output \m {\Hat {\M {H}}}.
%
\stopitemize
}

@@

@@

\stoptext

\DispNum {t:::01:Nh} {
\NC \V {t}
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {1} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
%
\NC \V {x}'
= \NC \startTheMatrix
\NC \T {\V {g}}' \NR
\NC \V {m} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
}
%
with
%
\DispNum {A:i:Ui:h1} {
\NC \M {A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
%
\NC \V {b}_i
= \NC \V {0}
\in \MB {R} ^{2 N_H^2} \NR
%
\NC \V {c}_i
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix
\in \MB {R} ^{3 N_H^2} \NR
%
\NC d_i
= \NC 0 \NR
%
\NC i 
= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
}

And
%
\DispNum {A:i:Ui:h1} {
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
\in \MB {R} ^{2 N_H^2} \NR
%
\NC \V {c}_i
= \NC \V {0}
\in \MB {R} ^{3 N_H^2} \NR
%
\NC d_i
= \NC \g_{\Rm {DS}} \NR
%
\NC i 
= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
}
